A Test of the Frequency Independence Assumption of the Power System Parameters used in Geomagnetically Induced Current Calculations

### 2019-02-11 paper.tex
update figs

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_raw_All_20060402.pdf}
\caption{(Top) One-second-cadence geomagnetic field measured at the Memanbetsu Magnetic Observatory (MMB). (Middle) One-second-cadence geoelectric field measured at the Memanbetsu Magnetic Observatory (MMB) $\sim$10 km from the Memanbetsu substation. (Bottom) One-second-cadence GIC measurements measured in a grounded neutral point of a Y-connected three-phase transformer connected to a 187 kV bus at the Memanbetsu substation of the Hokkaido Power Co. The subscripts $x$, $y$, and $z$ correspond to North, East, and Downward, respectively.}
\label{sample}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_TF_aves_SN-options-1.pdf}
\caption{Signal-to-noise ratios at the evaluation frequencies for the four models.}
\label{SN}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_TF_aves_aobo_histograms-options-1.pdf}
\caption{Distribution of parameters in Model 1. Each set of parameters were computed 35 times using one day of 1-second cadence data. The circle/dot on the horizontal axis indicates the average of each histogram: $a_o$ = 71.9 A/(V/km) and $b_o$ = -70.0 A/(V/km).}
\label{histogram}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_TF_aves_H-options-1.pdf}
\caption{Impulse responses for Models 1, 2, and 4. The circles at $t = 0$ correspond to the impulse response for Model 1; the red/blue lines are the impulse responses for Model 2 and 4. The values of $a_o$ and $b_o$ have been scaled by a factor of 10 for readability.}
\label{H}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_TF_aves_Z-options-1.pdf}
\caption{Frequency domain transfer functions for Models 1-3. By definition, the frequency domain transfer functions for $A_o$ and $B_o$ are constant and equal to $a_o$ and $b_o$.}
\label{Z}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_TF_aves_Phi-options-1.pdf}
\caption{Frequency domain phase values for Models 1-3.}
\label{Phi}
\end{figure}

@@

>>>>

@@

\clearpage

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_raw_All_20060805.pdf}
\caption{(Top) One-second-cadence geomagnetic field measured at the Memanbetsu Magnetic Observatory (MMB). (Middle) One-second-cadence geoelectric field measured at the Memanbetsu Magnetic Observatory (MMB) $\sim$10 km from the Memanbetsu substation. (Bottom) One-second-cadence GIC measurements measured in a grounded neutral point of a Y-connected three-phase transformer connected to a 187 kV bus at the Memanbetsu substation of the Hokkaido Power Co. The subscripts $x$, $y$, and $z$ correspond to North, East, and Downward, respectively.}
\label{sample}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_SN-options-1.pdf}
\caption{Signal-to-noise ratios at the evaluation frequencies for the four models.}
\label{SN}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_aobo_histograms-options-1.pdf}
\caption{Distribution of parameters in Model 1. Each set of parameters were computed 35 times using one day of 1-second cadence data. The circle/dot on the horizontal axis indicates the average of each histogram: $a_o$ = 71.9 A/(V/km) and $b_o$ = -70.0 A/(V/km).}
\label{histogram}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_H-options-1.pdf}
\caption{Impulse responses for Models 1, 2, and 4. The circles at $t = 0$ correspond to the impulse response for Model 1; the red/blue lines are the impulse responses for Model 2 and 4. The values of $a_o$ and $b_o$ have been scaled by a factor of 10 for readability.}
\label{H}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_Z-options-1.pdf}
\caption{Frequency domain transfer functions for Models 1-3. By definition, the frequency domain transfer functions for $A_o$ and $B_o$ are constant and equal to $a_o$ and $b_o$.}
\label{Z}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_Phi-options-1.pdf}
\caption{Frequency domain phase values for Models 1-3.}
\label{Phi}
\end{figure}
